The \dealii Library, Version 9.6

### 2024-09-24 9.6/paper.tex
Remove reference to deal.II-FROSch interface.
FECouplingValues.

    Historically, different places within the library implemented their own
    ad-hoc orientation logic, data encodings, and default values. We cleaned up
    this subsystem and instead of using three different booleans
    (\emph{orientation}, \emph{rotation}, and \emph{flip}), bitsets, or several
    other encodings, we now use a single \texttt{unsigned char} which we named the
    \emph{combined orientation}. Since the representation in some library
    interfaces has changed, most of the old interfaces have been deprecated and
    a few (such as the low-level interface to periodic boundary conditions) had
    to be incompatibly altered or removed.
\item The \texttt{SolverGMRES} class now offers a third orthogonalization
  method, the classical Gram--Schmidt method with delayed orthogonalization
  \cite{Bielich2022}. Furthermore, the solver now specifies the maximal basis
  size of the Arnoldi basis, rather than the number of auxiliary
  vectors. Some changes have also been made to the GMRES and F-GMRES
  implementations, making them use the same underlying kernels as much as possible.
\item The new class \texttt{FE\_Hermite} implements a Hermite interpolation basis of
  maximum regularity. These bases are always of odd polynomial degree $p$ and have
  regularity $r=(p-1)/2$.
\end{itemize}
%
The
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}{changelog}
-- listing more than 180 features and bugfixes --
contains a complete record of all changes; see \cite{changes96}.

@@

\begin{itemize}
\item The performance of the non-nested multigrid infrastructure
(\texttt{MGTwoLevelTransferNon\-Nested}) has been improved significantly by avoiding
redundant copy operations. Furthermore, support for simplex-shaped cells and
multiple-component elements has been added.
\item Several minor performance improvements in \dealii's evaluator class on
  sets of unstructured points, \texttt{FEPointEvaluation}, have been
  made. The changes are particularly useful for evaluating several quantities on the
  same set of points, which is enabled by \texttt{NonMatching::MappingInfo}.
\item We added the new class \texttt{FERemoteEvaluation}.
This is a class to access data
in a distributed matrix-free loop for non-matching discretizations.
Interfaces are named in analogy to \texttt{FEEvaluation}, in order to seamlessly switch the
local evaluator functionality at quadrature points of a computation. The key component is the
underlying MPI communication infrastructure, which is performed via \texttt{RemotePointEvaluation}.
Tutorial \step{89} has been added to present its usage
in the context of the application to acoustic conservation equations~\cite{heinz2023high}.
\item FECouplingValues

\todo[inline]{Luca: Please complete}
\end{itemize}

>>>>

    Historically, different places within the library implemented their own
    ad-hoc orientation logic, data encodings, and default values. We cleaned up
    this subsystem and instead of using three different booleans
    (\emph{orientation}, \emph{rotation}, and \emph{flip}), bitsets, or several
    other encodings, we now use a single \texttt{unsigned char} which we named the
    \emph{combined orientation}. Since the representation in some library
    interfaces has changed, most of the old interfaces have been deprecated and
    a few (such as the low-level interface to periodic boundary conditions) had
    to be incompatibly altered or removed.
\item The \texttt{SolverGMRES} class now offers a third orthogonalization
  method, the classical Gram--Schmidt method with delayed orthogonalization
  \cite{Bielich2022}. Furthermore, the solver now specifies the maximal basis
  size of the Arnoldi basis, rather than the number of auxiliary
  vectors. Some changes have also been made to the GMRES and F-GMRES
  implementations, making them use the same underlying kernels as much as possible.
\item The new class \texttt{FE\_Hermite} implements a Hermite interpolation basis of
  maximum regularity. These bases are always of odd polynomial degree $p$ and have
  regularity $r=(p-1)/2$.

\end{itemize}
%
The
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_5_2_and_9_6_0.html}{changelog}
-- listing more than 180 features and bugfixes --
contains a complete record of all changes; see \cite{changes96}.

@@

\begin{itemize}
\item The performance of the non-nested multigrid infrastructure
(\texttt{MGTwoLevelTransferNon\-Nested}) has been improved significantly by avoiding
redundant copy operations. Furthermore, support for simplex-shaped cells and
multiple-component elements has been added.
\item Several minor performance improvements in \dealii's evaluator class on
  sets of unstructured points, \texttt{FEPointEvaluation}, have been
  made. The changes are particularly useful for evaluating several quantities on the
  same set of points, which is enabled by \texttt{NonMatching::MappingInfo}.
\item We added the new class \texttt{FERemoteEvaluation}.
This is a class to access data
in a distributed matrix-free loop for non-matching discretizations.
Interfaces are named in analogy to \texttt{FEEvaluation}, in order to seamlessly switch the
local evaluator functionality at quadrature points of a computation. The key component is the
underlying MPI communication infrastructure, which is performed via \texttt{RemotePointEvaluation}.
Tutorial \step{89} has been added to present its usage
in the context of the application to acoustic conservation equations~\cite{heinz2023high}.

\item The \texttt{FECouplingValues} class provides a powerful tool for
 integrating finite element data between two different objects, even if they
 live on separate grids or have different topological dimensions (e.g., cells,
 faces, edges). This is particularly useful in the following scenarios: 
 \begin{itemize}
  \item Non-local Differential Operators: Evaluating fractional laplacian or
  boundary element methods.  
  \item Non-matching Discretizations: Integrating data between two independent
  discretization schemes that overlap on some areas. 
  \item Bulk-surface Coupling: Combining data from a bulk discretization and
  surface discretization.
 \end{itemize}

This class enables the combination of degrees of freedom indices, shape
functions, and quadrature points from two existing \texttt{FEValuesBase}
objects. The way this combination is performed is controlled by user-provided
\texttt{DoFCouplingType} and \texttt{QuadratureCouplingType} objects, which
define how the degrees of freedom and quadrature points are combined.

The flexibility offered by these coupling types allows users to:

\begin{itemize}
 \item Rearrange quadrature points in a tensor product structure for double
integration.
\item Reorder quadrature points to easily access shape function values and
gradients from two different finite element spaces located on the same point.
\item Identify and integrate over a reordered subset of the quadrature points.
\end{itemize}
\end{itemize}
